### 2022-04-09 manuscript.tex
ref [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/a8b484c207053ab9518e450fd19345960cfa9065.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/a8b484c207053ab9518e450fd19345960cfa9065/checks
https://github.com/scherzerthesis/thesis/actions/runs/2140984476

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/7a02dfb8a9274d8e9859aa2cf500dd7720d847a5/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/7a02dfb8a9274d8e9859aa2cf500dd7720d847a5}{scherzerthesis/thesis@7a02dfb}
on April 8, 2022.

@@

The mutational landscape of lung adenocarcinoma is complex due to the lifelong bombardment of DNA by carcinogens ingested into the distal lung epithelium{[}23770567{]}.
While understanding which altered genes play causal roles in tumor formation and progression is required for personalized medicine, the noisy mutation profiles in lung adenocarcinoma make it hard to do so.
However, there is a central role for the MAPK pathway during the initiation and progression of lung adenocarcinoma (Cicchini et al., 2017).
Oncogenic BRAF\textsuperscript{V600E} is a significant driver of lung adenocarcinoma.
However, mouse models with activation of BRAF \textsuperscript{V600E} only lead to benign tumorigenesis(Dankort et al., 2007; Shai et al., 2015).
Although it is known that activation of WNT and PI3k signaling and loss of \emph{Trp53} and \emph{Cdkn2a} genes allow BRAF\textsuperscript{V600E} benign lung tumors to progress to malignant disease, it is a time-consuming and laborious process to effects individual tumor suppressors, in GEMMs.
Therefore, we sought to systematically test a variety of known tumor suppressors in lung adenocarcinoma.
Furthermore, until now, we did not know the absolute number of cells in a BRAF\textsuperscript{V600E} adenoma, only its area, which is confounded by tissue sectioning and stromal cell contamination.
Prior to Tuba-Seq, it was challenging to accurately determine the size of BRAF\textsuperscript{V600E} adenomas.
Based on population doublings and cross-sections of BRAF \textsuperscript{V600E} tumors in histological sections, it is estimated that BRAF\textsuperscript{V600E}-driven lung adenomas grow about 15-20 populations doublings and reach a size of 1mm\textsuperscript{3}(Juan et al., 2014).
With Tuba-Seq, we accurately discerned the absolute size of all BRAF\textsuperscript{V600E} lung adenomas, regardless of size.
Interestingly, our results have revealed that BRAF\textsuperscript{V600E}-driven tumors widely differ in absolute tumor cell number. Our results support the hypothesis that each tumor-initiating cell has unique barriers to tumor outgrowth.
This heterogeneous response to BRAF\textsuperscript{V600E} activation likely reflects intrinsic differences between individual cell states.
Indeed, tumorigenic potential can vary significantly due to different cell types (AT2 vs.~Club cell vs.~AT1) or be influenced by subtle differences within a cell type, such as proximity to supporting stromal cells such as fibroblast or immune cells.
Since we used a ubiquitous promoter to drive BRAF\textsuperscript{V600E} and CAS9 expression, not all sequence likely reads come from adenomas or tumors but from average cell turnover during tissue homeostasis.
Therefore, in our quantification and analysis, we focused on tumors greater than 5,000 cells.

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/a8b484c207053ab9518e450fd19345960cfa9065/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/a8b484c207053ab9518e450fd19345960cfa9065}{scherzerthesis/thesis@a8b484c}
on April 9, 2022.

@@

The mutational landscape of lung adenocarcinoma is complex due to the lifelong bombardment of DNA by carcinogens ingested into the distal lung epithelium(Lawrence et al., 2013).
While understanding which altered genes play causal roles in tumor formation and progression is required for personalized medicine, the noisy mutation profiles in lung adenocarcinoma make it hard to do so.
However, there is a central role for the MAPK pathway during the initiation and progression of lung adenocarcinoma (Cicchini et al., 2017).
Oncogenic BRAF\textsuperscript{V600E} is a significant driver of lung adenocarcinoma.
However, mouse models with activation of BRAF \textsuperscript{V600E} only lead to benign tumorigenesis(Dankort et al., 2007; Shai et al., 2015).
Although it is known that activation of WNT and PI3k signaling and loss of \emph{Trp53} and \emph{Cdkn2a} genes allow BRAF\textsuperscript{V600E} benign lung tumors to progress to malignant disease, it is a time-consuming and laborious process to effects individual tumor suppressors, in GEMMs.
Therefore, we sought to systematically test a variety of known tumor suppressors in lung adenocarcinoma.
Furthermore, until now, we did not know the absolute number of cells in a BRAF\textsuperscript{V600E} adenoma, only its area, which is confounded by tissue sectioning and stromal cell contamination.
Prior to Tuba-Seq, it was challenging to accurately determine the size of BRAF\textsuperscript{V600E} adenomas.
Based on population doublings and cross-sections of BRAF \textsuperscript{V600E} tumors in histological sections, it is estimated that BRAF\textsuperscript{V600E}-driven lung adenomas grow about 15-20 populations doublings and reach a size of 1mm\textsuperscript{3}(Juan et al., 2014).
With Tuba-Seq, we accurately discerned the absolute size of all BRAF\textsuperscript{V600E} lung adenomas, regardless of size.
Interestingly, our results have revealed that BRAF\textsuperscript{V600E}-driven tumors widely differ in absolute tumor cell number. Our results support the hypothesis that each tumor-initiating cell has unique barriers to tumor outgrowth.
This heterogeneous response to BRAF\textsuperscript{V600E} activation likely reflects intrinsic differences between individual cell states.
Indeed, tumorigenic potential can vary significantly due to different cell types (AT2 vs.~Club cell vs.~AT1) or be influenced by subtle differences within a cell type, such as proximity to supporting stromal cells such as fibroblast or immune cells.
Since we used a ubiquitous promoter to drive BRAF\textsuperscript{V600E} and CAS9 expression, not all sequence likely reads come from adenomas or tumors but from average cell turnover during tissue homeostasis.
Therefore, in our quantification and analysis, we focused on tumors greater than 5,000 cells.

@@

\leavevmode\vadjust pre{\hypertarget{ref-IBUQd6mv}{}}%
Lawrence, M.S., Stojanov, P., Polak, P., Kryukov, G.V., Cibulskis, K., Sivachenko, A., Carter, S.L., Stewart, C., Mermel, C.H., Roberts, S.A., et al. (2013). Mutational heterogeneity in cancer and the search for new cancer-associated genes. Nature \emph{499}, 214--218. \url{https://doi.org/10.1038/nature12213}.
